Benchmarks

### 2021-09-21 analysis/benchmarks.Rmd
fix: load bmrk_aggr and set p.value

```{r benchmarks_setup, message = FALSE}
library("targets")
library("mlr3viz")
library("viridis")
library("ggplot2")
tar_load(bmrk_results)
```

@@

@@

@@

```{r benchmarks_aggr_critdiff_c_harrell}
autoplot(
    bmrk_aggr, type = "cd", meas = "harrell_c", minimize = FALSE, style = 2,
    p.value = 0.1
) + scale_color_viridis(discrete = TRUE)
```

>>>>

```{r benchmarks_setup, message = FALSE}
library("targets")
library("mlr3viz")
library("viridis")
library("ggplot2")
tar_load(bmrk_results)
tar_load(bmrk_aggr)

p.value <- 0.2
```

@@

Aggregated performance across all `nrow(bmrk_results$tasks)` datasets.

@@

# Pairwise comparison

*p*-value is set to `r p.value`
(otherwise an error is thrown because of insignificant results).

```{r benchmarks_aggr_pairwise_harrell_c}
autoplot(
    bmrk_aggr, type = "fn", meas = "harrell_c", p.value = p.value,
    col = palette.colors(2L)[2L]
)
```

@@

*p*-value is set to `r p.value`
(otherwise an error is thrown because of insignificant results).

```{r benchmarks_aggr_critdiff_c_harrell}
autoplot(
    bmrk_aggr, type = "cd", meas = "harrell_c", style = 2, p.value = p.value,
    minimize = FALSE
) + scale_color_viridis(discrete = TRUE)
```
